---
title: "simpleRegress"
author: "Dawn Bradford"
date: "Spring 2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set up regression models

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```
# NECK
## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
new <- data.frame(NECK=bears$NECK [c(5,15,23)])
predict(simp,new,se.fit=TRUE)
```


# HEADWTH
# MODEL LENGTH - HEADWTH
```{r}
simpHW <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHW)
summary.lm(simpHW)
```


```{r}
new <- data.frame(HEADWTH=bears$HEADWTH [c(5,15,23)])
predict(simpHW,new,se.fit=TRUE)
```


# HEADLEN
# MODEL LENGTH - HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simpHL)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(5, 15, 23)])
predict(simpHL,new,se.fit=TRUE)
```


# WEIGHT
# MODEL LENGTH - WEIGHT

```{r}
simpW <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simpW)
```

```{r}
new <- data.frame(WEIGHT=bears$WEIGHT [c(5, 15, 23)])
predict(simpW,new,se.fit=TRUE)
```

# CHEST
# MODEL LENGTH - CHEST

```{r}
simCT <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simCT)
```


```{r}
new <- data.frame(CHEST=bears$CHEST [c(5, 15, 23)])
predict(simCT,new,se.fit=TRUE)
```

# CONCLUSIONS


The best model was based on HEADLEN as seen by the adjusted R-squared , the prediction of the length for bears 5, 15, and 23 is  
70.31, 51.94, 58.83.       


The actual lengths of the bears was   
(62, 52, 54)

This error in prediction for bear number 5 is about 8 inches, for bear number 15 it is right on and bear number 23 the error in the prediction is just under 6 inches.  



